---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(RedisBaseContainer)


if(FALSE){
  library(readr)
  fileName <- "README.md"
  knitr::knit("inst/vignette.Rmd", output = fileName)
  fileName <- fileName
  content <- readChar(fileName, file.info(fileName)$size)
  content <- gsub("---.+?---","",content)
  content <- gsub("^(\r\n)+","",content)
  content <- gsub("([a-zA-Z]+)\\.jpg","vignettes/\\1.jpg",content)
  write_file(content, file = fileName)
}
```


This package is an extension package for the `DockerParallel` package and defines the common functions for the container class. It cannot be directly used by the end user. The user should use the package `doRedisContainer` and `RedisParamContainer`.

# doRedisContainer
The package `doRedisContainer` provides the worker container with foreach doRedis backend. The user can create the container object by
```{r, eval=FALSE}
library(doRedisContainer)
workerContainer <- doRedisWorkerContainer(image = "r-base")
```
The argument `image` determines the base image used by the container. The server container can be obtained by
```{r, eval=FALSE}
serverContainer <- doRedisServerContainer()
```

# RedisParamContainer
The package `RedisParamContainer` provides the worker container with BiocParallel RedisParam backend. The user can create the container object by
```{r, eval=FALSE}
library(RedisParamContainer)
workerContainer <- RedisParamWorkerContainer(image = "r-base")
```
The argument `image` determines the base image used by the container. The server container can be obtained by
```{r, eval=FALSE}
serverContainer <- RedisParamServerContainer()
```
